Abstract

### 2025-10-06 output/Main_text.Rmd
Update figure 1 referencing
Add panel labels, update figure title, and add footnote.

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     4.7
#| fig.width:      6.65
#| warning:        false
(plot_orth_uncorr_contours + plot_orth_corr) /
  (plot_oblique_ts + plot_cov_based_orth) +
  plot_layout(guides = "collect")

@@

>>>>

```{r item-plot-out}
#| cache:          false
#| fig.cap:        |
#|   Item vector plots with uncorrelated (a) and correlated latent dimensions.
#|   The latter coordinates are computed with
#|   (b) the agnostic multidimensional parameters, or
#|   with the covariance/correlation-based ones, which are then plot either
#|   (c) in an oblique basis, appropriate for the covariance structure, or
#|   (d) in the canonical basis.
#| fig.topcaption: true
#| fig.height:     4.7
#| fig.width:      6.65
#| warning:        false
(plot_orth_uncorr_contours + plot_orth_corr) /
  (plot_oblique_ts + plot_cov_based_orth) +
  plot_layout(guides = "collect")

@@

```{r format-contour-plot-props}
contour_breaks_out <- CONTOUR_BREAKS |>
  percent() |>
  glue_collapse(sep = ', ', last = ', and ')
```

::: {custom-style="FigureNote"}
*Note.* The items are represented along with
a standard bivariate normal distribution, with null correlation (a),
or with correlation $`r CORR_OBL_OUT`$ (b-d).
The contour plots represent the `r contour_breaks_out` of the maximum density,
from outer to inner, respectively.
:::
